Describing the scale and composition of calls for police service: a replication and extension using open data

### 2022-02-15 paper.Rmd
update paper

These descriptive findings provided data-driven evidence to suggest that the police indeed spend considerable amounts of time dealing with incidents in a social rather than solely crime-fighting capacity. This has implications to and beyond policing practice. Findings directly contribute to the fierce and politically-charged debate around the role and responsibilities of police officers in contemporary society. Both @ratcliffe2021policing and @lum2021can were published amidst the backdrop of the killing of George Floyd in May, 2020 and subsequent 'defund the police' protests across the US. Evidence which demonstrates that the public rely on the police for social duties beyond law enforcement suggests that a radical reduction in their role and responsibilities (e.g., through defunding) would increase demand on other social services. Should such radical reform take place without first understanding the scale and composition of public demand for the police, and without preemptively providing appropriate substitutes, there will be no supply to meet this shift in demand. Thus, @ratcliffe2021policing and @lum2021can contributed important empirical data to the (ongoing) discussion on police reform in the US.

@@

In replication and extension of the main findings reported by @ratcliffe2021policing and @lum2021can this contribution has described the scale and composition of calls for police service in Detroit, US. Broadly speaking, the results presented here provide robustness to those reported by @ratcliffe2021policing and @lum2021can. There is now substantial empirical evidence to demonstrate that, in multiple jurisdictions, the public rely on the police for both social _and_ crime-fighting functions. A reduction in the capacity of the police to meet this emergency demand, without first providing appropriate, capable and accessible replacement emergency services, could have considerable implications for public safety and well-being. This contribution provides the first such demonstration using open data and open code, opening up analyses for scrutiny, re-use, and extension by the public, academics and/or police practitioners. We encourage usage of the materials provided with this study to replicate analyses across other jurisdictions. In doing so, we hope to see a consistent and reliable evidence-base across different contexts for the purposes of comparison and generalization.

>>>>

These descriptive findings provided data-driven evidence to suggest that the police indeed spend considerable amounts of time dealing with incidents in a social rather than solely crime-fighting capacity. This has implications to and beyond policing practice. Findings directly contribute to the fierce and politically-charged debate around the role and responsibilities of police officers in contemporary society. Both @ratcliffe2021policing and @lum2021can were published amidst the backdrop of the killing of George Floyd in May, 2020 and subsequent 'defund the police' protests across the US. Evidence which demonstrates that the public relies on the police for social duties beyond law enforcement suggests that a radical reduction in their role and responsibilities (e.g., through defunding) would increase demand on other social services. Should such radical reform take place without first understanding the scale and composition of public demand for the police, and without preemptively providing appropriate substitutes, there will be no supply to meet this shift in demand. Thus, @ratcliffe2021policing and @lum2021can contributed important empirical data to the (ongoing) discussion on police reform in the US.

@@

In replication and extension of the main findings reported by @ratcliffe2021policing and @lum2021can this contribution has described the scale and composition of calls for police service in Detroit, US. Broadly speaking, the results presented here provide robustness to those reported by @ratcliffe2021policing and @lum2021can. There is now substantial empirical evidence to demonstrate that, in multiple jurisdictions, the public relies on the police for both social _and_ crime-fighting functions. A reduction in the capacity of the police to meet this emergency demand, without first providing appropriate, capable and accessible replacement emergency services, could have considerable implications for public safety and well-being. This contribution provides the first such demonstration using open data and open code, opening up analyses for scrutiny, re-use, and extension by the public, academics and/or police practitioners. We encourage usage of the materials provided with this study to replicate analyses across other jurisdictions. In doing so, we hope to see a consistent and reliable evidence-base across different contexts for the purposes of comparison and generalization.
